---
title: "R function that computes all the main descriptive statistics"
format: html
editor: visual
author:
  - name: Simon-Pierre Boucher
    orcid: 0000-0002-3756-3937
    email: simon-pierre.boucher.1@ulaval.ca
    affiliations:
      - name: Université Laval
        address: 2325 Rue de l'Université
        city: Québec
        state: QC 
        postal-code: G1V 0A6
---

This function computeDescriptiveStats takes a numeric vector data as input and computes:

* Mean
* Median
* Variance
* Standard Deviation
* Skewness
* Kurtosis
* Minimum
* Maximum
* Range (minimum and maximum)
* Quantiles (default quantiles include 0%, 25%, 50%, 75%, 100%)

To use this function, you need to have R installed on your system, and you should ensure that the e1071 package is installed as well. You can test this function by copying the code into an R script or R console. The set.seed(123) part ensures that the random data generated is the same every time you run the script for reproducibility purposes.

##### Load necessary library
```{r}
if (!require(e1071)) install.packages("e1071")
library(e1071)
```


##### Define the function
```{r}
computeDescriptiveStats <- function(data) {
  if (!is.numeric(data)) {
    stop("Data must be numeric")
  }
  
  stats <- list(
    mean = mean(data),
    median = median(data),
    variance = var(data),
    standard_deviation = sd(data),
    skewness = skewness(data),
    kurtosis = kurtosis(data),
    minimum = min(data),
    maximum = max(data),
    range = range(data),
    quantiles = quantile(data)
  )
  
  return(stats)
}
```


##### Test the function with random data

```{r}
set.seed(123) # For reproducibility
random_data <- rnorm(100) # Generate 100 random numbers from a normal distribution
```


##### Compute descriptive statistics
```{r}
descriptive_stats <- computeDescriptiveStats(random_data)
```


# Print the results
```{r}
print(descriptive_stats)
```
