---
title: "Logit regression with R"
format: html
editor: visual
categories:
  - Logit model
  - Generalized Least Squares
  - GLM() package
author:
  - name: Simon-Pierre Boucher
    orcid: 0000-0002-3756-3937
    email: simon-pierre.boucher.1@ulaval.ca
    affiliations:
      - name: Université Laval
        address: 2325 Rue de l'Université
        city: Québec
        state: QC 
        postal-code: G1V 0A6
---

# Generating simulated data for logistic regression model
### Set seed for reproducibility

```{r}
set.seed(123)
```

### Number of observations

```{r}
n <- 100
```

### Generate predictor variables x1, x2, and x3

```{r}
x1 <- rnorm(n)
x2 <- rnorm(n)
x3 <- rnorm(n)
```

### Generate a binary outcome variable y based on predictor variables with logistic relation

```{r}
p <- 1 / (1 + exp(-(0.5*x1 + 0.8*x2 - 0.3*x3 + rnorm(n))))
y <- rbinom(n, 1, p)
```

### Create a dataframe containing all variables

```{r}
data <- data.frame(y, x1, x2, x3)
```

# Estimating a logistic regression model
### Specifying the logistic regression model using glm()
### Syntax: glm(outcome ~ predictor1 + predictor2 + ..., data = data_frame, family = binomial)

```{r}
model <- glm(y ~ x1 + x2 + x3, data = data, family = binomial)
```

### Print summary of the model

```{r}
summary(model)
```