---
title: "ARMA regression with R"
format: html
editor: visual
categories:
  - Logit model
  - Generalized Least Squares
  - GLM() package
author:
  - name: Simon-Pierre Boucher
    orcid: 0000-0002-3756-3937
    email: simon-pierre.boucher.1@ulaval.ca
    affiliations:
      - name: Université Laval
        address: 2325 Rue de l'Université
        city: Québec
        state: QC 
        postal-code: G1V 0A6
---
# Load necessary library for ARMA models

```{r}
library(forecast)
```

# Set seed for reproducibility

```{r}
set.seed(123)
```

# Generating simulated data for AR(1) model
### Number of observations

```{r}
n <- 100
```

### Generate AR(1) time series with AR coefficient = 0.7 and white noise

```{r}
ar1_data <- arima.sim(n = n, model = list(ar = 0.7))
```

# Estimating AR(1) model

```{r}
ar1_model <- Arima(ar1_data, order = c(1, 0, 0))
```

# Print summary of AR(1) model

```{r}
summary(ar1_model)
```

# Generating simulated data for MA(1) model
### Generate MA(1) time series with MA coefficient = 0.5 and white noise

```{r}
ma1_data <- arima.sim(n = n, model = list(ma = 0.5))
```

# Estimating MA(1) model

```{r}
ma1_model <- Arima(ma1_data, order = c(0, 0, 1))
```

# Print summary of MA(1) model

```{r}
summary(ma1_model)
```

# Generating simulated data for ARMA(1,1) model
### Generate ARMA(1,1) time series with AR coefficient = 0.6, MA coefficient = 0.4, and white noise

```{r}
arma11_data <- arima.sim(n = n, model = list(ar = 0.6, ma = 0.4))
```

# Estimating ARMA(1,1) model

```{r}
arma11_model <- Arima(arma11_data, order = c(1, 0, 1))
```

# Print summary of ARMA(1,1) model

```{r}
summary(arma11_model)
```