---
title: "OLHC plot with R"
format: html
editor: visual
categories:
  - Logit model
  - Generalized Least Squares
  - GLM() package
author:
  - name: Simon-Pierre Boucher
    orcid: 0000-0002-3756-3937
    email: simon-pierre.boucher.1@ulaval.ca
    affiliations:
      - name: Université Laval
        address: 2325 Rue de l'Université
        city: Québec
        state: QC 
        postal-code: G1V 0A6
---

### Load the necessary package

```{r}
library(quantmod)
```

### Set the ticker symbol for Apple

```{r}
symbol <- 'AAPL'
```

### Import data from Yahoo Finance

### The 'getSymbols' function directly assigns the data to a variable in the environment with the same name as the symbol

```{r}
getSymbols(symbol, src = 'yahoo', auto.assign = TRUE)
```

### Plotting the data

### 'chartSeries' is a function from the quantmod package that provides various financial charts, including OLHC

### Here, we use it to plot the OLHC data for AAPL

#### Start by specifying the chart type as 'auto' which automatically selects the best chart type based on the data

#### The 'theme' argument allows customization of the chart appearance. 'chartTheme' with 'black' creates a dark-themed chart

```{r}
chartSeries(AAPL, type = 'auto', theme = chartTheme('black'))
```

### The result is a comprehensive chart displaying the Open, Low, High, and Close prices of Apple stock
